Testing Methodologies for a Multiplayer Game Protocol\\

### 2020-12-03 paper/PaperDraft2.tex
Remote Testing, some additional outlining

\title{Testing Methodologies for Asynchronous Centralized Simulations\\
}

@@

These are all concerns of our case study, NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
 to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.

@@

Before we may continue to discuss testing methodologies for centralized simulations, we should take a look at what exactly a centralized asynchronous simulation is. 
In this section, we will take a look at the high-level overview of such a simulation before delving into the specific type of data utilized by NodeTank.

\subsection{Architecture}

In attempting to understand the architecture of a centralized simulation, we must also understand under which cirmucstances such an architecture is desired. For example,
let's assume that we have some data that we would like to share between one or more clients, with a client being a receiver which is interested in some data. At a very high level, such
a data sharing layout can be split into two categories: peer-peer and client-server. Smed et. al[6] describes the different layouts in detail, however, generally a peer-peer architecture 
is defined as having two or more clients which have all, or part of some data which is then shared equally each peer. In this scenario, each client is equal to every other client, and thus,
would have to be fully connected to one another[6]. This type of architecture has its own advantages when it comes to certain types of systems, such as file sharing and lock-step simulations,
however we cannot maintain the type of centralized simulation which is pertinent to our topic.

@@

\subsection{Trained Model Approach}

Discuss the setup for the trained model - the tools and automatic invocation

\section{Case Study}

Discuss the specificics of the game architecture here - show the actual code and frameworks

\section{Conclusion}

@@

\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016, 
Available from ProQuest Dissertations & Theses Global. (1881527059). 
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924

@@

[3] R. Rezin, ”Model Checking in multiplayer games development”, Innopolis University, 
2017, Available: https://arxiv.org/pdf/1712.01207.pdf

@@

[5] J.Peusaari, “Distributed Issues in Real-Time Interactive Simulations”, Department of Technology Lappeenranta University of Technology, Finland,
 Available: https://ieeexplore.ieee.org/abstract/document/5361761

[6] J. Smed, "Aspects of Networking in Multiplayer Computer Games", Proceedings of International Conference on Application and Development of Computer Games in the 21st Century, Hong Kong, 2001,
Available: https://www.researchgate.net/publication/269251176_Aspects_of_Networking_in_Multiplayer_Computer_Games
\end{document}

>>>>

\title{Testing Methodologies for a Multiplayer Game Protocol\\
}

@@

These are all concerns of NodeTank. While they may be to a lesser degree, as NodeTank is a game rather than a tool for executing experiments for research, they will be valid concerns
 to the degree of their perceptibility. As delays grow, corresponds to the players’ abilities to enjoy the experience decline.

@@

As this protocol will work with 3D graphical data, we need to present some prerequisite ideas that the reader may not be
familiar with. Since the purpose of this paper is not to discuss how 3D graphics work, the explanation will be kept brief
as to only build up the necessary intuition.

@@

\subsection{Remote Testing}

\subsubsection{Core RPC Services}Remote testing of the target application is achieved through an adaptable and extensible pair of RPC services. Two APIs, 'Data' and 'RemoteCtrl', that enable remote testing and they are capable of being updated and expanded quite easily as the application's range of behaviors grow during its lifetime. Each API service is defined in an IDL(Interface Description Language) file. Each defines the a service's name followed by generic a list call signatures of the functions that shoould be exposed by the service. The IDL offers several plain data types such booleans, floating points, a string type, and signed integers of the typical varying bit-widths. Basic C-style structures and enumerations may also be defined to add versatility to the services defined types.
\subsubsection{RPC Adaptability}As the application grows and new types of interactions and information need to be handled, the same pair of IDL need only minor editing by the maintainer. Automatic generations scripts may be rerun at each stage of changing demand. The resulting output is a fully-formed supporting library in the target programming language of choice for, both, the client and server sides of each RPC service. The RPC-server half of each API is included and/or linked to from the simulation's server to allow both services awareness of and access to all necessary data of the simulation's clients. In the event of new or changing data types, the client simulation needs only to be rebuilt in the case of a compiled-language and no changes are required for interpreted languages. In the case of new or changing functions, the auto-generated RPC handlers need only be given function bodies by the tester. Building remote testing utilities for the simulation is easily done thanks to this process, as there are no dependencies between the programming language of the simulation's server and the RPC client. The RPC service itself manages all translation between native data types of the server and it's RPC client. This means the RPC service manages the serialization/deserialization and transport of all function arguments and return values, byte-order translation between differing host hardware, and member alignment between differing host operating environments. All these features allow for a simulation written in javascript, C++, Java, Python, C\#, etc. to agnostically cooperate with any client written in any other supported language and host operating environemnt.
\subsubsection{Distributibility}With an underlying TCP or UDP transport layer, this remote testing strategy allows for a wide range of geographical testing configurations to be thuroughly explored. Testing and examination of the system may be performed in a close-proximity LAN configuration, or the simulation server and its clients may be much more georgraphically separated, communicating over the Internet with one another and the testing client itself.

\section{Case Study}
\subsection{Remote RPC Services}
\subsubsection{Remote Testing Service}
\paragraph{Hooks into the javascript testing framework}
\subsubsection{Remote Control Service}
\paragraph{Injecting user input}
\paragraph{Extracting the rendered environment}

\section{Conclusion}
\subsection{Future Work}

@@

\section{References}
[1] A. Valadares, “Aspect-oriented architectural style for distributed interactive simulations”, 2016,
Available from ProQuest Dissertations \& Theses Global. (1881527059).
Retrieved from https://search-proquest-com.huaryu.kl.oakland.edu/docview/1881527059?accountid=12924

@@

[3] R. Rezin, ”Model Checking in multiplayer games development”, Innopolis University,
2017, Available: https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=8432324

@@

[5] J.Peusaari, “Distributed Issues in Real-Time Interactive Simulations”, Department of Technology Lappeenranta University of Technology, Finland,
 Available: https://ieeexplore.ieee.org/abstract/document/5361761
\end{document}
